Pricing Approaches for Green Tea Products

### 2024-11-21 paper/paper.qmd
Corrected reference for improved spacing and correct capitalization

The graphing scripts in this paper are written in R[@citeR], with the tidyverse package[@tidyverse] The graphs are generated with ggplot2[@ggplot2].Data cleaning was done in SQL[@citeSQL].

@@

### Missing Data
There where many data points missing due to problems during data collection and relatively late start of data collection for many products. This may cause challenges in drawing accurate conclusions or identifying trends, as the incomplete dataset might not represent the true patterns or variability within the data. The gaps could introduce biases, skewing results and potentially affecting the reliability of analyses. Furthermore, the late start of data collection for certain products might result in insufficient time for capturing seasonal or time-sensitive changes, further limiting the accuracy of the findings. It is known[@charlebois2024grocers] that price freeze during November to February is a common practice, however this data is unable to capture this and similar seasonal patterns as the interval is out of scope.

>>>>

The graphing scripts in this paper are written in R [@citeR], with the tidyverse package [@tidyverse] The graphs are generated with ggplot2 [@ggplot2].Data cleaning was done in SQL [@citeSQL].

@@

### Missing Data
There where many data points missing due to problems during data collection and relatively late start of data collection for many products. This may cause challenges in drawing accurate conclusions or identifying trends, as the incomplete dataset might not represent the true patterns or variability within the data. The gaps could introduce biases, skewing results and potentially affecting the reliability of analyses. Furthermore, the late start of data collection for certain products might result in insufficient time for capturing seasonal or time-sensitive changes, further limiting the accuracy of the findings. It is known [@charlebois2024grocers] that price freeze during November to February is a common practice, however this data is unable to capture this and similar seasonal patterns as the interval is out of scope.
